\large How resource abundance and resource stochasticity affect organisms' range sizes

### 2025-02-17 writing/manuscript.Rmd
changed "Figure" to "fig."; checked diffs

\noindent Our simulations are based on a simplistic environment with many assumptions that allowed us to estimate how resource abundance and stochasticity affect organisms' home-range sizes if organisms can only respond to changes by adapting the amount of time spent searching for food (with no energetic cost to movement). The use of continuous-time movement models coupled with few drivers of movement supported realistic data that could be explained by straightforward causal models. The absence of confounding variables (e.g., predator avoidance, territoriality, competition, landscape connectivity; see Figure \@ref(fig:dag-sims)) or sample size limitation allowed us to ensure estimates were accurate and robust (sensitivity analysis available in Appendix B).

>>>>

\noindent Our simulations are based on a simplistic environment with many assumptions that allowed us to estimate how resource abundance and stochasticity affect organisms' home-range sizes if organisms can only respond to changes by adapting the amount of time spent searching for food (with no energetic cost to movement). The use of continuous-time movement models coupled with few drivers of movement supported realistic data that could be explained by straightforward causal models. The absence of confounding variables (e.g., predator avoidance, territoriality, competition, landscape connectivity; see fig. \@ref(fig:dag-sims)) or sample size limitation allowed us to ensure estimates were accurate and robust (sensitivity analysis available in Appendix B).
